Nested sampling with two objective functions

### 2015-11-04 Paper/ms.tex
Fixed error

\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/joint2.pdf}
\caption{\it The same as Figure~\ref{fig:joint1}. The selected particle
at $(2.65, 1.31)$ has a corner count of 1. The particle at
$(2.53, 0.84)$ can be thought of as a single-particle standard Nested Sampling
run restricted to $L_1 < 2.65$ which is attempting to increase $L_1$.
\label{fig:joint2}}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/joint2.pdf}
\caption{\it The same as Figure~\ref{fig:joint1}. The selected particle
at $(2.65, 1.31)$ has a corner count of 1. The particle at
$(2.53, 0.84)$ can be thought of as a single-particle standard Nested Sampling
run restricted to $L_1 < 2.65$ which is attempting to increase $L_2$.
\label{fig:joint2}}
\end{figure}
